---
title: "VDJ trimming/insertion regression by race for DNTT"
output:
  html_document:
    fig_crop: no
    toc: true
    toc_depth: 2
    dev: 'svg'
fig_width: 26
fig_height: 10 
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(Cairo)
knitr::opts_chunk$set(dev = "png", dev.args = list(type = "cairo-png"), fig.path = "/home/mrussel2/tcr-gwas/trimming_regression/scripts_by_race/figures", dpi = 600,fig.width=20, fig.height=10) 
#knitr::opts_chunk$set(dpi = 600,fig.width=26, fig.height=10) 
TRIM_TYPE = 'all_insert'
source("/home/mrussel2/tcr-gwas/trimming_regression/scripts/manha_visualization.R")
setDTthreads(1)
subset = 'dntt'
plotting_cutoff = 'False'

```

```
All insertion regressions for DNTT without PCA correction:
```{r ALL_DNTT_insertions_no_pca, echo=TRUE, warning=FALSE}
manhattan_plot_cluster(trim_type = 'all_insert', plotting_cutoff, gene_annotations = 'True', maf_cutoff = 0.05, pca_structure_correction = 'False', pca_type = 'none', subset = 'dntt')
```

All insertion regressions for DNTT with PCA correction:
```{r ALL_DNTT_insertions_pca, echo=TRUE, warning=FALSE}
manhattan_plot_cluster(trim_type = 'all_insert', plotting_cutoff, gene_annotations = 'True', maf_cutoff = 0.05, pca_structure_correction = 'True', pca_type = '8_pc_air', subset = 'dntt')
```

